### 2010-08-09 docs/runtime_parameters/runtime_parameters.tex
update to latest _parameters

@@

@@

@@

@@

@@

@@

@@

@@

\verb=  use_eos_coulomb  = &    &  .true. \\

@@

>>>>

\verb=  amr_buf_width  = &   the number of buffer zones surrounding a cell tagged for refinement. note that this needs to be >= regrid\_int  &  -1 \\

@@

\verb=  barrier_timers  = &   Call a parallel\_barrier before each of the simple timers we have coded in advance.f90.  Might cause a very slight overall performance hit.  &  .false. \\

@@

\verb=  conductivity_constant  = &   the constant conductivity (only applies if the conductivity/constant module is used)  &  1.0d0 \\

@@

\verb=  do_planar_invsq_grav  = &   are we doing 1/r$^2$ gravity for plane-parallel  &  .false. \\

@@

\verb=  octant  = &   set octant = T if you just want to model an octant of a sphere (note: only takes effect for spherical geometry)  &  .false. \\

@@

\verb=  planar_invsq_mass  = &   the point mass for planar 1/r$^2$ gravity  &  0.d0 \\
\verb=  plot_Hext  = &   plot external heating (Hext) in plotfile  &  .false. \\

@@

\verb=  plot_eta  = &   plot $\etarho$ in plotfile  &  .false. \\

@@

\verb=  plot_omegadot  = &   plot omegadot in plotfile  &  .true. \\

@@

\verb=  use_eos_coulomb  = &   use the Coulomb corrections between ions (if supported by the EOS)  &  .true. \\

@@

\verb=  use_hypre  = &   use the hypre library  &  .false. \\
